---
title: "Documentation and Example for Rdatdota"
author: "Huxianzhi Lin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Documentation and Example for Rdatdota}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, echo = FALSE, results='hide'}
setwd("C:/Users/lhxz/Documents/GitHub/Rdatdota/R")
temp = list.files(pattern="*.R")
lapply(temp, source)
```

Rdatdota is an R datdota API client specifically designed for Valve's game Dota2.  

Rdatdota should be used in strict accordance with datdota's [Terms of service and Privacy Policy](http://datdota.com/about)

## get_* Family Funtions

The get_* family functions are the functions used to access the API. They map the following API methods:

Dota 2 methods relating to match information:

* get_heroes    
  A data.frame of Dota2 Heroes.  
* get_hero_players    
  A list of the most frequent players of particular heroes.  
* get_match  
  Information about a particular match.  
* get_match_length  
  Three lists of the duration of matches  
* get_player_avg     
  A list of average player performances  
* get_player_single     
  A list of player performance in a single match  
* get_player_records      
  Lists of player records  
* get_player_unique     
  A list of players and the unique heroes they have used
* get_team  
  Lists of team performances

Datdota don't provide API documentation. You can directly visit their [website](www.datdota.com) to use their UI.  

All get_* functions have several common arguments that can be used:

* after - The beginning date of the match. The default value is "2011.01.01".  

* before - The last day of the period to search. The default value is "2018.07.12".  

* duration - The time the game lasts (measured in minutes). The default value is "0-100".  

* tier - What tier of event is this? 1 = Premium; 2 = Professional; 3 = Semi-pro; (Connected by "&"). The default value is "1&2&3".  

* patch - Which patches are you interested in? From 6.74 to 7.20 (Connected by "&"). The default value is "7.19"   

* split - What type of event was it? Choose from "online", "lan" or "post-event". The default value is "lan".  

* leagues -  What league is it in? Check the number of the league on www.datdota.com.  The default value is NULL.

* valve - Is this a Valve event? Choose from "yes", "no" or "does-not-matter". The default value is "does-not-matter".  

Moreover, all get_* functions will return a datdota_api object that contains 3 elements:

* url - The request url.
* content - This is the useful element to the user, since it contains Dota2 data.
* response - This shows information about the response retrieved from datdota like headers, status, cookies, date, etc.  

The above are true for all the get_* functions, so they will not be analysed in detail in the individual function demonstration that follows.  

### get_hero_players  
`get_hero_players` returns a list of the most frequent players of particular heroes. The function does not require any extra arguments and outputs a list with the following factors: 

* hero: The serial number of the hero.  
* games: Number of use.  
* rank: Rank among users. Includes 1, 2 and 3.  
* players: A list contains players.  
* steam ID: The steam ID of the player.  
* nickname: The nickname of the player.  

```{r eval = TRUE}
str(get_hero_players()$content[[1]][1])
```

### get_heroes
`get_heroes` returns a list of Dota2 Heroes. The fuction requires following specific arguments:  

* threshold: The min game count.
* players: Players to search for. Check the serial number of the players on www.datdota.com. (Connected by "&". Can be null.)
* teams: Teams to serch for. Check the serial number of the players on www.datdota.com. (Connected by "&". Can be null.)
* heroes: Heroes picked. Check the serial number of the heroes on www.datdota.com. (Connected by "&". Can be null.)
* roles: What role was it played? Choose from "core" or "support". (Connected by "&". Can be null.)  

The output is a list with the following factors:  

* hero: The serie number of the hero.
* wins: Wins.
* losses: Losses.
* total: Times of pick.
* gamesRadiant: Times that the hero is in Radient team.
* gamesDire: Times that the hero is in Dire team.
* Winrate: Winrate.
* kills: Times of kill.
* deaths: Times of Death.
* assists: Times of Assistance.
* gpm: Gold per minute.
* xpm: EXP per minute.
* lastHits: Times of last hit.
* denies: Times of deny.
* avgKAL: Undocumented.
* kda: (Kills + Assists)/Deaths.
* level: Level.
* heroDamage: Hero damage.
* towerDamage: Tower damage.
* heroHealing: Hero heal.
* goldSpemt: Gold spent.

```{r eval = TRUE}
str(get_heroes()$content[[1]][1])
```
### get_match
`get_match` returns a list of matches. The fuction requires following specific arguments: 

* teams_a One side of the team to serch for. Check the serial number of the players on www.datdota.com. (Connected by "&". Can be null.)
* teams_b The other side of the team to serch for. Check the serial number of the players on www.datdota.com. (Connected by "&". Can be null.)
*  heroes_a Heroes that team A chose. Check the serial number of the heroes on www.datdota.com. (Connected by "&". Can be null.)
*  heroes_b Heroes that team B chose. Check the serial number of the heroes on www.datdota.com. (Connected by "&". Can be null.)  

The output is a list with the following factors:  

* matchID: The match ID.
* radTeamID: The radient team ID.
* direTeamID: The dire team ID.
* radPicks: A list contains 5 hero numbers that the radient team pick.
* direPicks: A list contains 5 hero numbers that the dire team pick
* radVictory: Whether radient team won.
* date: Date of the match.
* leagueID: League ID.
* leagueName: League name.
* radName: Radient team name.
* direName: Dire team name.
* rad: Undocumented.
* dire: Undocumented..
* radIsA: Undocumented.
* duration: Duration.

```{r eval = TRUE}
str(get_match()$content[[1]][[1]][1])
```
### get_match_length
`get_match_length` returns three lists of the duration of matches. The fuction requires following specific arguments: 

* teams: Teams to serch for. Check the serial number of the players on www.datdota.com. (Connected by "&". At least one must appear)

The output are three lists. The first list is called durations which tells the distribution of the minutes. The second list is called longest which includes the match id, teams and duration. The third list is called shortest which includes the match id, teams and duration. There are also three variables in the content list which provides the mean, the standard deviation and the count.

* minute: The time the game lasts.
* percentile: Percentage.
* match: The match ID.
* teams: Two teams of this match.
* duration: The time the game lasts.
* mean: Average time of these matches.
* stdDev Standard deviation.
* count: Total number of matches.

```{r}
str(get_match_length()$content[[1]][[1]][1])
str(get_match_length()$content[[1]][[2]][1])
str(get_match_length()$content[[1]][[3]][1])
str(get_match_length()$content[[1]][4])
str(get_match_length()$content[[1]][5])
str(get_match_length()$content[[1]][6])

```
### get_player_avg
`get_player_avg` returns a list of average player performances. The fuction requires following specific arguments: 

* players: Players to search for. Check the serial number of the players on www.datdota.com. (Connected by "&". Can be null.)
* teams: Teams to serch for. Check the serial number of the players on www.datdota.com. (Connected by "&". Can be null.)
* heroes: Heroes picked. Check the serial number of the heroes on www.datdota.com. (Connected by "&". Can be null.)
* roles: What role was it played? Choose from "core" or "support". (Connected by "&". Can be null.)  

The output is a list with the following factors:  

* steamID: The steam ID of the player.
* nickname: The nickname of the player.
* wins: Wins.
* losses: Losses.
* total: Times of pick.
* gamesRadiant: Times that the hero is in Radient team.
* gamesDire: Times that the hero is in Dire team.
* Winrate: Winrate.
* kills: Times of kill.
* deaths: Times of Death.
* assists: Times of Assistance.
* gpm: Gold per minute.
* xpm: EXP per minute.
* lastHits: Times of last hit.
* denies: Times of deny.
* avgKAL: Undocumented.
* kda: (Kills + Assists)/Deaths.
* level: Level.
* heroDamage: Hero damage.
* towerDamage: Tower damage.
* heroHealing: Hero heal.
* goldSpemt: Gold spent.

```{r eval = TRUE}
str(get_player_avg()$content[[1]][[1]])
```
### get_player_records
`get_player_records` returns lists of records. The fuction requires following specific arguments: 

* players: Players to search for. Check the serial number of the players on www.datdota.com. (Connected by "&". Can be null.)
* teams: Teams to serch for. Check the serial number of the players on www.datdota.com. (Connected by "&". Can be null.)
* heroes: Heroes picked. Check the serial number of the heroes on www.datdota.com. (Connected by "&". Can be null.)
* roles: What role was it played? Choose from "core" or "support". (Connected by "&". Can be null.)  

The content element of the list contains a sub list called data. Following lists are included: kills, gpm, hero_damage, denies, kda_1_death, kills_per_min, assists_per_min, gold, last_hits, xpm, assists, tower_damage, hero_healings, deaths, deaths_per_min. There are sub lists in every one of these lists, each represents one record. The record in turn represents the steam ID of the player, the nickname of the player, the value of the record, the hero ID, the match ID.

* kills: Kills.
* gpm: Gold per minute.
* hero_damage: The total hero damage.
* denies: Total number of denies.
* kda_1_death: KDA.
* kills_per_min: Kills per minute.
* assists_per_min: Assists per minute.
* gold: Overall gold.
* last_hits: Total number of last hits.
* xpm: EXP per minute.
* assists: Total number of assists.
* tower_damage: Total tower damage.
* hero_healing: Total hero healing.
* deaths: Total number of death.
* deaths_per_min: Deaths per minute.

```{r eval = TRUE}
str(get_player_records()$content[[1]]$kills[[1]])
```
### get_player_single
`get_player_single` returns a list of player performance in a single match

* players: Players to search for. Check the serial number of the players on www.datdota.com. (Connected by "&". Can be null.)
* teams: Teams to serch for. Check the serial number of the players on www.datdota.com. (Connected by "&". Can be null.)
* heroes: Heroes picked. Check the serial number of the heroes on www.datdota.com. (Connected by "&". Can be null.)
* roles: What role was it played? Choose from "core" or "support". (Connected by "&". Can be null.)  

The output is a list with the following factors:  

* steamID: The steam ID of the player.
* nickname: The nickname of the player.
* matchID: The match ID.
* hero: The hero that the player use.
* victory: Whether win or not.
* kills: Times of kill.
* deaths: Times of Death.
* assists: Times of Assistance.
* gpm: Gold per minute.
* xpm: EXP per minute.
* lastHits: Times of last hit.
* denies: Times of deny.
* avgKAL: Undocumented.
* kda: (Kills + Assists)/Deaths.
* level: Level.
* heroDamage: Hero damage.
* towerDamage: Tower damage.
* heroHealing: Hero heal.
* goldSpemt: Gold spent.
* endItems: Lists of the items at the end of the match.

```{r eval = TRUE}
str(get_player_single()$content[[1]][[1]])
```
### get_player_unique
`get_player_unique` returns a list of players and the unique heroes they have used.

* players: Players to search for. Check the serial number of the players on www.datdota.com. (Connected by "&". Can be null.)
* teams: Teams to serch for. Check the serial number of the players on www.datdota.com. (Connected by "&". Can be null.)
* roles: What role was it played? Choose from "core" or "support". (Connected by "&". Can be null.)

The output is a list with the following factors:  

* steamID: The steam ID of the player.
* nickname: The nickname of the player.
* heroes: A list of unique heroes that the player have played.
* countUnique: The number of unique heroes that the player have used.
* gameCount: Total nuber of games.

```{r eval = TRUE}
str(get_player_unique()$content[[1]][[1]])
```
### get_team
`get_player_teams` returns lists of team performances

* teams: Teams to serch for. Check the serial number of the players on www.datdota.com. (Connected by "&". Can be null.)

The output is lists with the following factors:  

* team: A list that contains the name, valveId, tag of the team.
* wins: Wins.
* losses: Losses.
* total: Total games.
* winrate: Winrate.
* gamesRadient: Times that the player is in Radient team.
* gamesDire: Times that the player is in Dire team.
* kills: Average times of kill.
* deaths: Average times of Death.
* assists: Average times of Assistance.
* gpm: Average gold per minute.
* xpm: Average EXP per minute.
* lastHits: Average times of last hit.
* denies: Average times of deny.
* duration: Average game duration.
* durationWins: Average game duration that the team won the game.
* durationLosses: Average game duration that the team lost the game.
* durationShift: Average duration shift.

```{r eval = TRUE}
str(get_team()$content[[1]][[1]])
```

### BUGS / FEATURES

If you would like to make any recommendations or give feedback or report a bug please visit the
development site on [github](https://github.com/HuxianzhiLin/Rdatdota).


You made it to the end of the documentation! Thanks for reading! 
